# Regression and model validation

*This week I learned how to use R to wrangling the data and make the linear regression analysis and evaluate the validation of modelling..*

- Describe your work and results clearly. 
- Assume the reader has an introductory course level understanding of writing and reading R code as well as statistical methods.
- Assume the reader has no previous knowledge of your data or the more advanced methods you are using.

```{r}

```

Here we go again...

In the exercise of data wrangling, the code is as following:

```{r}
lrn14<- read.table('http://www.helsinki.fi/~kvehkala/JYTmooc/JYTOPKYS3-data.txt', sep='\t', header = TRUE)
dim(lrn14)
str(lrn14)

```

This dataset has 183 rows (the observations) and 60 columns (the variables).

```{r}
lrn14$Attitude
lrn14$Attitude/10

library(dplyr)
deep_questions <- c("D03", "D11", "D19", "D27", "D07", "D14", "D22", "D30", "D06",  "D15", "D23", "D31")
surface_questions <- c("SU02","SU10","SU18","SU26", "SU05","SU13","SU21","SU29","SU08","SU16","SU24","SU32")
strategic_questions <- c("ST01","ST09","ST17","ST25","ST04","ST12","ST20","ST28")

deep_columns <- select(lrn14, one_of(deep_questions))
lrn14$deep <- rowMeans(deep_columns)
surface_columns <- select(lrn14, one_of(surface_questions))
lrn14$surf <- rowMeans(surface_columns)
strategic_columns <- select(lrn14, one_of(strategic_questions))
lrn14$stra <- rowMeans(strategic_columns)

keep_columns <- c("gender","Age","Attitude", "deep", "stra", "surf", "Points")
learning2014 <- select(lrn14, one_of(keep_columns))
str(learning2014)

colnames(learning2014)
colnames(learning2014)[2] <- 'age'
colnames(learning2014)[3] <- 'attitude'
colnames(learning2014)[7] <- 'points'

learning2014 <- filter(learning2014, points > 0)
str(learning2014)
head(learning2014)
write.csv(learning2014,file= 'learning2014')
read.csv('learning2014')

```


In the exercise 2, the Code is as following:

```{r}
students2014 <- read.table('http://s3.amazonaws.com/assets.datacamp.com/production/course_2218/datasets/learning2014.txt', sep = ',', header = TRUE)
dim(students2014)
str(students2014)
```

This data files includes 166 rows (observations) and 7 columns(variables), which means there are 7 kinds of index for 166 students.The variables includes gender, age, attuitude, deep, dtra, surf, and points.

```{r}
library(ggplot2)
p1 <- ggplot(students2014, aes(x=attitude, y=points, col=gender))
p2 <- p1 + geom_point()
p2
p3 <- p2+geom_smooth(method = 'lm')
p4 <- p3+ggtitle('attitude of students versus exam points')
p4

pairs(students2014[-1])

library(GGally)
library(ggplot2)

p <- ggpairs(students2014, mapping=aes(col=gender, alpha=0.3),lowe=list(combo=wrap('facethist', bins=20)))
p
```

 There is an extremely significant positive relationship between attitude of students and points.For male,age is negative related with points.

```{r}
my_model1 <- lm (points ~ attitude + stra + surf, data = students2014)
summary(my_model1)

my_model2 <- lm (points ~ attitude + stra, data = students2014)
summary(my_model2)
```

In the first regression model, points as the target varable together with attitude, stra and surf as explantory variables, the model can be used because the P value is less than 0.001(extremely significant) even though there is no significantly relationships between stra, surf and points.

Model2 can explain the 20.74% changes of points.

```{r}
par(mfrow=c(2,2))
plot(my_model2, which=c(1,2,5))
```


The data is mostly Gaussian distribution, according to the linear qq plots. The model is sensible based on these three plots.

