# Logistic Regression and cross validation

---
title: "chapter3.Rmd"
name: 'siqizhao'
output: html_document
font_size: 12pt
---
```{r}

alc <- read.table('http://s3.amazonaws.com/assets.datacamp.com/production/course_2218/datasets/alc.txt', sep=',', header = TRUE)

```


In this data set, there are 35 variables and 382 observations in total.The variables are: school,sex,age,address,famsize,Pstatus,Medu,Fedu,Mjob,Fjob reason,nursery,internet,guardian,traveltime studytime,failures,schoolsup,famsup,paid activities,higher,romantic,famrel,freetime goout,Dalc,Walc,health,absences,G1,G2,G3,alc_use,high_use.




I chose failures, absences,traveltime and activities as explainary variables to explore the relationsips between them and the target variable-high_use.The results are as below(three of them have significatly positive relationship with high_use):
high_use=0.4176*failures-1.0157
high_use=0.0683*absences-1.2640
high_use=0.4290*traveltime-1.5146



So, the high_use valus will increase with the increase of failures, absences and traveltime. However, there is no significant relationship between activities and high_use.


```{r}
library(ggplot2)
library(tidyr)
library(dplyr)
gather(alc) %>% glimpse
gather(alc) %>% ggplot(aes(value)) + facet_wrap("key", scales = "free") + geom_bar()
g1 <- ggplot(alc, aes(x = high_use, y = failures, col = sex))
g1 + geom_boxplot() + ylab("failures")
g2 <- ggplot(alc, aes(x = high_use, y = absences, col = sex))
g2 + geom_boxplot() + ggtitle("Student absences by alcohol consumption and sex")
```



If we look at the combined bar chart, we can find the numbers of students who attend extra-curricular activities and the students who don't are almost close, which can tell us the non-significat relationship between activities and high_use is sensible.Let's use the same principle to explain the other relationships, and the results should be consistent with the original hypothese.


Based on the results of Logistic regression analysis between failures&absences&traveltime&activities and high_use, the fitted model is as below:



(Intercept)      failures      absences    traveltime activitiesyes 
-1.86181552    0.36618544    0.07004812    0.42610620   -0.32180313 

 OR     2.5 %    97.5 %
(Intercept)   0.1553903 0.0828279 0.2841262
failures      1.4422227 1.0755782 1.9361180
absences      1.0725598 1.0374448 1.1130908
traveltime    1.5312834 1.1164457 2.1057338
activitiesyes 0.7248409 0.4542950 1.1528149

high_use= 0.36619 * failures+0.07005 * absences + 0.42611 * travelime -1.86182

There is no significat relationship between activities and high_use, which is same with the previous hypothese, and should be removed fromt the whole model.

The 2x2 cross tabulation of predictions is as below:

   prediction
     
high_use   FALSE   TRUE

   FALSE       261        9
   
   TRUE         87        25



```{r}
m5 <- glm(high_use ~ failures+absences+traveltime, data = alc, family = "binomial")
probabilities <- predict(m5, type = "response")
alc <- mutate(alc, probability = probabilities)
alc <- mutate(alc, prediction = probability > 0.5)
select(alc, failures, absences, traveltime, high_use, probability, prediction) %>% tail(10)
table(high_use = alc$high_use, prediction = alc$prediction)
g <- ggplot(alc, aes(x = probability, y = high_use, col = prediction))
g + geom_point()
table(high_use = alc$high_use, prediction = alc$prediction) %>% prop.table %>% addmargins
```


According to the 10-folds cross-validation on your mode, I got a smaller error (0.2591623) than Datacamp, which means that my model has better test set performance.




I made two different fited model with more predictors;model6 has 5 predictors which are failures,absences,traveltime,higher as well as sex; while model 7 has 4 explainary factors.

The 10 folds cross validation results are as below:

m6-> 0.2408377
m7-> 0.2382199

Compared with m5 (0.2591623), the errors of m7 is the smallest one which has one more predictor than m5.The fitted model is:

(Intercept)    failures    absences  traveltime        sexM 
-2.51975566  0.36718070  0.07462037  0.39558320  0.96465837

high_use= 0.36718070 * failures + 0.07462037 * absences + 0.39558320 * traveltime + 0.96465837 * sexM -2.51975566








