# Clustering and classification

---
title: "chapter4"
output: html_document
---

The boston data frame has 506 rows and 14 columns, which means that there are 14 variables. crim is per capita crime rate by town; zn is proportion of residential land zoned for lots over 25,000 sq.ft.; indus is the proportion of non-retail business acres per town; chas is Charles River dummy variable (= 1 if tract bounds river; 0 otherwise); nox is nitrogen oxides concentration (parts per 10 million); rm is average number of rooms per dwelling; age is proportion of owner-occupied units built prior to 1940; dis is weighted mean of distances to five Boston employment centres;rad is index of accessibility to radial highways; tax is full-value property-tax rate per \$10,000; ptratio is pupil-teacher ratio by town.black is 1000(Bk - 0.63)^2 where Bk is the proportion of blacks by town; lstat means lower status of the population (percent); medv means median value of owner-occupied homes in \$1000s.

According to the correlation matrix, there is an obverse positive relationship between rad and tax, indus and nox, while there is an negative relationship between dis and nox, indus as well as dis. Also, seems like there are no obverse correlations between chas and all the others.

```{r}

# access the MASS package
library(MASS)

# load the data
data("Boston")

# center and standardize variables
boston_scaled <- scale(Boston)

# summaries of the scaled variables
summary(boston_scaled)

# class of the boston_scaled object
class(boston_scaled)

# change the object to data frame
boston_scaled <- as.data.frame(boston_scaled)

# summary of the scaled crime rate
summary(boston_scaled$crim)

# create a quantile vector of crim and print it
bins <- quantile(boston_scaled$crim)
bins

# create a categorical variable 'crime'
crime <- cut(boston_scaled$crim, breaks = bins, include.lowest = TRUE, labels = c("low", "med_low", "med_high", "high"))

# look at the table of the new factor crime
table(crime)

# remove original crim from the dataset
boston_scaled <- dplyr::select(boston_scaled, -crim)

# add the new categorical value to scaled data
boston_scaled <- data.frame(boston_scaled, crime)

# number of rows in the Boston dataset 
n <- nrow(boston_scaled)

# choose randomly 80% of the rows
ind <- sample(n,  size = n * 0.8)

# create train set
train <- boston_scaled[ind,]

# create test set 
test <- boston_scaled[-ind,]

# save the correct classes from test data
correct_classes <- test$crime

# remove the crime variable from test data
test <- dplyr::select(test, -crime)

```
After scaling the dataset, all the numbers become much smaller than oringinal ones and all the mean values are zero.

```{r}
# linear discriminant analysis
lda.fit <- lda(crime ~ ., data = train)

# print the lda.fit object
lda.fit

# the function for lda biplot arrows
lda.arrows <- function(x, myscale = 1, arrow_heads = 0.1, color = "orange", tex = 0.75, choices = c(1,2)){
  heads <- coef(x)
  arrows(x0 = 0, y0 = 0, 
         x1 = myscale * heads[,choices[1]], 
         y1 = myscale * heads[,choices[2]], col=color, length = arrow_heads)
  text(myscale * heads[,choices], labels = row.names(heads), 
       cex = tex, col=color, pos=3)
}

# target classes as numeric
classes <- as.numeric(train$crime)

# plot the lda results
plot(lda.fit, dimen = 2, col = classes, pch = classes)
lda.arrows(lda.fit, myscale = 1)

# predict classes with test data
lda.pred <- predict(lda.fit, newdata = test)

# cross tabulate the results
table(correct = correct_classes, predicted = lda.pred$class)

```





```{r}

r = getOption("repos")
r["CRAN"] = "http://cran.us.r-project.org"
options(repos = r)

# access the MASS package
library(MASS)

data('Boston')

# center and standardize variables
boston_scaled <- scale(Boston)

# euclidean distance matrix
dist_eu <- dist(boston_scaled)

# look at the summary of the distances
summary(dist_eu)

# manhattan distance matrix
dist_man <- dist(boston_scaled, method = 'manhattan')

# look at the summary of the distances
summary(dist_man)

# k-means clustering
km <-kmeans(boston_scaled, centers = 3)

# plot the Boston dataset with clusters
pairs(boston_scaled, col = km$cluster)

## Bonus

# k-means clustering
km <-kmeans(boston_scaled, centers = 3)

# plot the Boston dataset with clusters
pairs(boston_scaled, col = km$cluster)

## Superbonus

model_predictors <- dplyr::select(train, -crime)

# check the dimensions
dim(model_predictors)
dim(lda.fit$scaling)

# matrix multiplication
matrix_product <- as.matrix(model_predictors) %*% lda.fit$scaling
matrix_product <- as.data.frame(matrix_product)

install.packages("plotly")

plotly::plot_ly(x = matrix_product$LD1, y = matrix_product$LD2, z =  matrix_product$LD3, type= 'scatter3d', mode='markers', color=train$crime)
```


