# Regression and model validation

*This week I learned how to use R to wrangling data and make the linear regression analysis and evaluate the validation of model.*

- Describe your work and results clearly. 
- Assume the reader has an introductory course level understanding of writing and reading R code as well as statistical methods.
- Assume the reader has no previous knowledge of your data or the more advanced methods you are using.

Here we go again...

In the exercise 2, the Code is as following:

This data files includes 166 rows (observations) and 7 columns(variables), which means there are 7 kinds of index for 166 students.The variables includes gender, age, attuitude, deep, dtra, surf, and points.

```{r}
students2014 <- read.table('http://s3.amazonaws.com/assets.datacamp.com/production/course_2218/datasets/learning2014.txt', sep = ',', header = TRUE)
dim(students2014)
str(students2014)

library(ggplot2)
p1 <- ggplot(students2014, aes(x=attitude, y=points, col=gender))
p2 <- p1 + geom_point()
p2
p3 <- p2+geom_smooth(method = 'lm')
p4 <- p3+ggtitle('attitude of students versus exam points')
p4

pairs(students2014[-1])

library(GGally)
library(ggplot2)

p <- ggpairs(students2014, mapping=aes(col=gender, alpha=0.3),lowe=list(combo=wrap('facethist', bins=20)))
p
```

There is an extremely significant positive relationship between attitude of students and points.For male,age is negative related with points.

```{r}
my_model1 <- lm (points ~ attitude + stra + surf, data = students2014)
summary(my_model1)

my_model2 <- lm (points ~ attitude + stra, data = students2014)
summary(my_model2)
```

In the first regression model, points as the target varable together with attitude, stra and surf as explantory variables, the model can be used because the P value is less than 0.001(extremely significant) even though there is no significantly relationships between stra, surf and points.

Model2 can explain the 20.74% changes of points.

```{r}
par(mfrow=c(2,2))
plot(my_model2, which=c(1,2,5))
```


The data is mostly Gaussian distribution, according to the linear qq plots. The model is sensible based on these three plots.


